### 2021-05-14 project_ashish_monograph/CMS.tex
progress

\begin{figure}[H]
  \centering
  \includegraphics[width=1\columnwidth]{./cmsdetector_merged.png}
  \caption{Left: 3D design of CMS detector showing various concentric layers. Right: \onehalfspacing Transverse view of the CMS detector showing the silicon tracker, electromagnetic calorimeter, hadron calorimete##r, superconducting solenoid and muon chambers \cite{Chatrchyan:2008aa}}
  \label{fig:CMSdetector}
\end{figure}

>>>>

\begin{figure}[H]
  \centering
  \includegraphics[width=1\columnwidth]{./cmsdetector_merged.png}
  \caption{Left: 3D design of CMS detector showing various concentric layers. Right: \onehalfspacing Transverse view of the CMS detector showing the silicon tracker, electromagnetic calorimeter, hadron calorimete##r, superconducting solenoid and muon chambers. \cite{Chatrchyan:2008aa}}
  \label{fig:CMSdetector}
\end{figure}

### 2021-05-14 project_ashish_monograph/PCC.tex
progress

The instantaneous luminosity per bunch crossing L is proportional to the number of proton-proton (pp) interactions per bunch crossing (pileup) and the proportionality constant is the ratio of  LHC orbit frequency f and the pp interaction cross section $\sigma_{interaction}$. \\

@@

L = $\frac{<N_{cluster}> \: f }{<N_{cluster/interaction}> \: \sigma_{interaction}}$ \\

@@

$\sigma_{vis}$ = $<N_{cluster/interaction}>$  $\sigma_{interaction}$

Thus, instantaneous luminosity per bunch crossing is given by \\

L = $\frac{<N_{cluster}> \: \sigma_{interaction} \: f }{ \:\sigma_{vis} \: \sigma_{interaction}}$ \\

>>>>

The instantaneous luminosity per bunch crossing L is proportional to the number of proton-proton (pp) interactions per bunch crossing (pileup) and the proportionality constant is the ratio of  LHC orbit frequency f and the pp interaction cross section $\sigma_{interaction}(\sqrt{s})$ where s is the proton-proton collision center-of-mass energy. \\

@@

L = $\frac{<N_{cluster}> \: f }{<N_{cluster/interaction}> \: \sigma_{interaction}(\sqrt{s})}$ \\

@@

$\sigma_{vis}$ = $<N_{cluster/interaction}>$  $\sigma_{interaction}(\sqrt{s})$ \\

\newpage Thus, instantaneous luminosity per bunch crossing is given by \\

L = $\frac{<N_{cluster}> \: \sigma_{interaction}(\sqrt{s}) \: f }{ \:\sigma_{vis} \: \sigma_{interaction}(\sqrt{s})}$ \\

### 2021-05-14 project_ashish_monograph/bkg.tex
progress

\section{Backgrounds}
\label{sec:bkg}
(background in vdM, afterglow backgrounds in Physics, subtraction of these) \\

N= \sigma \:L + N_{background} \\
L = $ \int L_{inst} \: dt = \int \frac{R(t)}{\sigma_{vis}} \:dt $  \\ \sigma = \sigma_{interaction} (\sqrt{s}) \: A \:\epsilon\\

N: total number of event including signal and background. \\
$\sigma_{vis}$: visible cross section for PCC.\\
$L_{inst}$: instantaneous luminosity.\\
$N_{background}$: Number of background events \\

The pixel cluster counting (PCC) method produces a small out-of-time response (OOTR, or afterglow).\\
Type 1: fake hits in the bunch crossing after the colliding bunches (signal charge spillover).\\
Type 2: Activated material in the detector due to the large radiation doses, exponentially decays for many bunch crossings.\\
Afterglow effects are tiny in the case of tracklets (2x and 3x coincidences).\\

@@

Figure 7 shows the afterglow noise induced by one colliding bunch. Since it is normalized to 1 at the first bin it means the first bin is the colliding bunch. The values at bins $>$ 1 are the cluster counts observed for bunches after the colliding bunch divided by the cluster counts observed by the colliding bunch. There are three parts to this distribution: \\

>>>>

\newpage \section{Backgrounds}
\label{sec:bkg}
(background in vdM, afterglow backgrounds in Physics, subtraction of these) \\

N= \sigma \:L + N_{background} \\

L = $ \int L_{inst} \: dt = \int \frac{R(t)}{\sigma_{vis}} \:dt $  \\

\sigma = \sigma_{interaction} (\sqrt{s}) \: A \:\epsilon\\

N: total number of event including signal and background. \\

$R(t) = \frac{d}{dt} <N_{cluster}>$ is the time dependent cluster rate. \\

$N_{background}$: Number of background events \\

$\sigma_{vis}$: PCC visible cross section.\\

$\sigma_{interaction}$ : proton-proton interaction cross section. \\

s: center of mass energy of colliding protons. \\

A: acceptance of the pixel detector. \\

$\epsilon$ : efficiency of the pixel detector. \\

$L_{inst}$: instantaneous luminosity.\\

The pixel cluster counting (PCC) method produces a small out-of-time response (OOTR, or afterglow) that has two types.\\

Type 1: fake hits in the bunch crossing after the colliding bunches (signal charge spillover).\\

Type 2: Activated material in the detector due to the large radiation doses, exponentially decays for many bunch crossings.\\

Afterglow effects are tiny in the case of tracklets (2x and 3x coincidences).\\

@@

Fig. 7 shows the afterglow noise induced by one colliding bunch. Since it is normalized to 1 at the first bin it means the first bin is the colliding bunch. The values at bins $>$ 1 are the cluster counts observed for bunches after the colliding bunch divided by the cluster counts observed by the colliding bunch. There are three parts to this distribution: \\

### 2021-05-14 project_ashish_monograph/results.tex
progress

\begin{figure}[H]
  \centering
  \includegraphics[width=0.5\columnwidth]{./316993.png}
  \caption{Top: Bunch crossing id (bcid) and PCC lumi as a function of lumi section. Bottom: PCC lumi as a function of lumi section (late RunD veto list is used) for run 2018A.}
  \label{fig:CMS}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.5\columnwidth]{./ls_lumi.png}
  \caption{PCC luminosity as a function of lumi section.}
  \label{fig:CMS}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.5\columnwidth]{./runs.png}
  \caption{PCC luminosity as a function of run number.}
  \label{fig:CMS}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.5\columnwidth]{./2018A_lumiratio.png}
  \caption{Luminosity ratios for different subdetectors L2, L3, L4, D1, D2, D3 of pixel detector as a function of lumi section for Run2018A.}
  \label{fig:CMS}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.5\columnwidth]{./ProfileXcombined_2018A.png}
  \caption{X Profile of luminosity ratio vs lumi section graph showing luminosity fraction as a function of lumi section.}
  \label{fig:CMS}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.5\columnwidth]{./319270.png}
  \caption{Top: Bunch crossing id (bcid) and PCC lumi as a function of lumi section. Bottom: PCC lumi as a function of lumi section (late RunD veto list is used) for run 2018B.}
  \label{fig:CMS}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.5\columnwidth]{./ls_lumi_2018B.png}
  \caption{PCC luminosity as a function of lumi section.}
  \label{fig:CMS}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.5\columnwidth]{./runs_2018B.png}
  \caption{PCC luminosity as a function of run number.}
  \label{fig:CMS}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.5\columnwidth]{./2018B_lumiratio.png}
  \caption{Luminosity ratios for different subdetectors L2, L3, L4, D1, D2, D3 of pixel detector as a function of lumi section for Run2018B.}
  \label{fig:CMS}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.5\columnwidth]{./ProfileXcombined_2018B.png}
  \caption{X Profile of luminosity ratio vs lumi section graph showing luminosity fraction as a function of lumi section.}
  \label{fig:CMS}
\end{figure}

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=0.5\columnwidth]{./2018C_lumiratio.png}
  \caption{Luminosity ratios for different subdetectors L2, L3, L4, D1, D2, D3 of pixel detector as a function of lumi section for Run2018C. }
  \label{fig:CMS}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.5\columnwidth]{./ProfileXcombined_2018C.png}
  \caption{X Profile of luminosity ratio vs lumi section graph showing luminosity fraction as a function of lumi section.}
  \label{fig:CMS}
\end{figure}

>>>>

\begin{figure}[H]
  \centering
  \includegraphics[width=0.52\columnwidth]{./316993.png}
  \caption{Top: Bunch crossing id (bcid) and PCC lumi as a function of lumi section. Bottom: PCC lumi as a function of lumi section (late RunD veto list is used) for run 2018A.}
  \label{fig:CMS}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.52\columnwidth]{./ls_lumi.png}
  \caption{PCC luminosity as a function of lumi section.}
  \label{fig:CMS}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.52\columnwidth]{./runs.png}
  \caption{PCC luminosity as a function of run number.}
  \label{fig:CMS}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.52\columnwidth]{./2018A_lumiratio.png}
  \caption{Luminosity ratios for various subdetectors L2, L3, L4, D1, D2, D3 of pixel detector as a function of lumi section for Run2018A.}
  \label{fig:CMS}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.52\columnwidth]{./ProfileXcombined_new.png}
  \caption{X Profile of luminosity ratio vs lumi section graph for various subdetectors L2, L3, L4, D1, D2, D3 of pixel detector showing luminosity fraction as a function of lumi section.}
  \label{fig:CMS}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.52\columnwidth]{./319270.png}
  \caption{Top: Bunch crossing id (bcid) and PCC lumi as a function of lumi section. Bottom: PCC lumi as a function of lumi section (late RunD veto list is used) for run 2018B.}
  \label{fig:CMS}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.52\columnwidth]{./ls_lumi_2018B.png}
  \caption{PCC luminosity as a function of lumi section.}
  \label{fig:CMS}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.52\columnwidth]{./runs_2018B.png}
  \caption{PCC luminosity as a function of run number.}
  \label{fig:CMS}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.52\columnwidth]{./2018B_lumiratio.png}
  \caption{Luminosity ratios for various subdetectors L2, L3, L4, D1, D2, D3 of pixel detector as a function of lumi section for Run2018B.}
  \label{fig:CMS}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.5\columnwidth]{./ProfileXcombinedB_new.png}
  \caption{X Profile of luminosity ratio vs lumi section graph for various subdetectors L2, L3, L4, D1, D2, D3 of pixel detector showing luminosity fraction as a function of lumi section.}
  \label{fig:CMS}
\end{figure}

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=0.5\columnwidth]{./2018C_lumiratio.png}
  \caption{Luminosity ratios for various subdetectors L2, L3, L4, D1, D2, D3 of pixel detector as a function of lumi section for Run2018C. }
  \label{fig:CMS}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.5\columnwidth]{./ProfileXcombinedC_new.png}
  \caption{X Profile of luminosity ratio vs lumi section graph for various subdetectors L2, L3, L4, D1, D2, D3 of pixel detector showing luminosity fraction as a function of lumi section.}
  \label{fig:CMS}
\end{figure}

### 2021-05-14 project_ashish_monograph/syst.tex
progress

\section{Systematics}
\label{sec:syst}
(main systematics: vdM, non-linearity, stability, check others in the PAS)

>>>>

\section{Systematics}
\label{sec:syst}
(main systematics: vdM, non-linearity, stability, check others in the PAS) \\

Systematic uncertainties in the bunch overlap widths along x and y directions measured during VdM scans can arise from length scale calibration, orbit drift, x-y correlations of bunch proton density function, emittance growth, bunch-bunch deflection, dynamic $\beta$ which tells us whether bunches are narrow or wide, bunch current calibration, ghosts and satellites, scan to scan variation, bunch to bunch variation, cross-detector consistency, afterglow effects, linearity and CMS deadtime.  \\

1. Length scale calibration:  Value of the separation derived from currents in the corrector magnets, calibrated against central tracking system and compare luminous region information (vertices distribution) versus nominal separation. \\

2. Emittance growth: Bunches size are known to increase in size during the fill. Effect is sizable during the ~30 minutes, Bias almost negligible if emittance grows linearly with time and if measurement are made in between X and Y scans. \\

3. Orbit drift: The beams can slowly drift in the transverse plane. This effect is typically small but can be harmful in some cases. Drift of the orbit estimated by BPM measurements taken between scans and extrapolated to interaction point. \\

4. xy-correlations: The VdM scan method assumes that the bunch proton density function is factorizable into independent x- and y-dependent terms which is not fully true and can lead to a biased estimate of the bunch overlap area. In order to measure this effect, special beam imaging scans are conducted. In these scans, the measured vertex position distributions are used to derive the bunch proton densities, which can then be used to estimate a correction to the visible cross section $\sigma_{vis}$. \\

5. Non-linearity: \\

6. Stability:  \\

7. Bunch-Bunch Effects: \\

Dipolar kick (bunch-bunch deflection): Repulsive force deflects beams affecting nominal separation depends on the separation itself, the beam width and the current. \\

 Quadrupolar (de)focusing (dynamic $\beta$): Effective beam width is modified depending on the separation which in turn affects the peak luminosity (rate) value. \\

### 2021-05-14 project_ashish_monograph/upgrade.tex
progress

\section{The TEPX upgrade for HL-LHC}
\label{sec:tepx}
(describe the TEPX detector design, algorithms clusters/coincidences, stat precision, linearity)\\

The High Luminosity (HL)-LHC will increase instantaneous luminosity to unprecedented values of $7 \times 10^{34} cm^{-2} s^{-1}$ which corresponds to 200 proton-proton collisions per bunch crossing (pileup). Run 2 pixel detector will not be able to handle the extreme radiation environment, resolve nearby particle tracks and operate properly for high pileup values. That is why Run 2 pixel detector will be replaced by a new pixel detector which will be composed of three subdetectors: tracker barrel pixel detector (TBPX), tracker forward pixel detector (TFPX) and tracker endcap pixel detector (TEPX).

\begin{figure}[H]
  \centering
  \includegraphics[width=0.6\columnwidth]{./up.png}
  \caption{\onehalfspacing Left: View in the x-y plane of the double disk structure of one TEPX disk. The sensors in blue and red correspond to the two double disks at slightly different z positions. Right: Example of two- and threefold coincidence regions on a portion of a single TEPX disk \cite{}.}
  \label{fig:CMS}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.6\columnwidth]{./up1.png}
  \caption{ \onehalfspacing Left: A layout of the CMS Phase-2 inner tracker with the location of TEPX Disk 4, Ring 1 highlighted in dark red. Right: The x-y view of TEPX disk 4, ring 1 \cite{}.}
  \label{fig:CMS}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.6\columnwidth]{./up2.png}
  \caption{ \onehalfspacing Schematic view for one quarter of the tracker, illustrating the location of TEPX. \cite{}.}
  \label{fig:CMS}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.6\columnwidth]{./tepx.png}
  \caption{ \onehalfspacing Sketch of the TFPX and TEPX layouts, showing one quarter of the detector in r-z view. Modules of type 1 $\times$ 2 are shown in green, while 2 $\times$ 2 modules are represented in orange. The two layers of modules that populate the front- and back-side of a disc and that overlap in $r-\phi$ can be seen by zooming into the figure in the online version. \cite{}.}
  \label{fig:CMS}
\end{figure}

@@

@@

>>>>

\newpage \section{The TEPX upgrade for HL-LHC}
\label{sec:tepx}
(describe the TEPX detector design, algorithms clusters/coincidences, D4R1 as HL-LHC luminometer, stat precision, linearity)\\

The High Luminosity (HL)-LHC will increase instantaneous luminosity to unprecedented value of $7.5 \times 10^{34} cm^{-2} s^{-1}$ which corresponds to 200 proton-proton collisions per bunch crossing (pileup). Run 2 pixel detector will not be able to handle the extreme radiation environment, resolve nearby particle tracks and operate properly to give a reliable estimate of the instantaneous luminosity for high pileup values. That is why it will be replaced by a new pixel detector which will be composed of three subdetectors: tracker barrel pixel detector (TBPX), tracker forward pixel detector (TFPX) and tracker endcap pixel detector (TEPX). TEPX will have better radiation tolerance, increased granularity, improved two-track separation, improved estimation of hit rate and statistical precision, extended tracking acceptance $|\eta|=4$ with Disk 4 Ring 1 operating as an independent luminometer. \\

Tracker endcap pixel detector (TEPX) consists of four double disks per side (-Z and +Z) as shown in Fig. 27 with each double disk containing five rings as shown in Fig. 28 having 20, 28, 36, 44 and 48 modules respectively. One double disk has four surfaces with +Z side containing modules with even module number in front layers (L1 $\&$ L2) and modules with odd module number in back layers (L3 $\&$ L4) from Ring 1 to Ring 4 and for Ring 5, modules with odd module number in front layers and modules with even module number in back layers as shown in Fig. 29. For -Z side, four surfaces contain modules with odd module number in front layer and modules with even module number in back layer from Ring 1 to Ring 4 and for Ring 5, modules with even module number in front layer and modules with odd module number in back layer. \\

Instantaneous luminosity determination using PCC method for Phase 2 HL-LHC can be based on counting the number of clusters or coincidences. The innermost ring of the last disk of TEPX (D4R1) is located at 2.65 m away from the interaction point that is beyond the tracking acceptance ($|\eta = 4|$) and as this region has few tracking points, it can be solely used for the purpose of luminosity measurement by using the full available trigger rate and bandwidth.  Two fold coincidences are those hits which are created by the module overlap regions between various layers of one TEPX double disk. Two fold coincidences are better way to distinguish between a real hit and random electrical noise. They are more likely to be real hit than random electrical noise. Two fold coincidence in $\phi$ will involve modules overlapping in the same ring in front and back layers of one double disk as shown in top part of Fig. 30 and Fig. 31 while two fold coincidence in r will require modules overlapping between successive rings in the front (L1 $\&$ L2) and back layers (L3 $\&$ L4) of one double disk as shown in bottom part of Fig. 30. Luminosity calculated based on counting coincidences has an advantage over clusters that afterglow effects are tiny in the case of coincidences. \\

Nonlinearity is one of the systematic uncertainty in the calculation of instantaneous luminosity using PCC and PCC visible cross section $\sigma_{vis}$. A Linear relation between the number of clusters and pileup (PU) would imply that\\

$<N_{cluster/interaction}> = \frac{<N_{cluster}>}{(PU)} = \frac{\sigma_{visible}}{\sigma_{interaction} (\sqrt{s})}$ \\

$<N_{cluster}> =  \frac{\sigma_{visible}}{\sigma_{interaction}(\sqrt{s})} (PU)$ \\

\newpage Linearity indicates that the PCC visible cross section $\sigma_{vis}$ does not depend on the per bunch instantaneous luminosity (ideal luminometer). In ideal  scenario, $\sigma_{vis}$ is not dependent on pileup, but this a potential problem with the luminometer. A non-linear relation $<N_{cluster}> = \alpha (PU)^{\gamma}, \gamma \neq 1$ would add non-linear terms in the rate equation $R = \sigma L$  and cause $\sigma_{vis}$ to vary with the per bunch instantaneous luminosity and pileup values.

\begin{figure}[H]
  \centering
  \includegraphics[width=0.8\columnwidth]{./tepx_geometry.png}
  \caption{ \onehalfspacing A layout of the CMS Phase-2 inner tracker showing four TEPX disks, eight TFPX disks and 4 barrel layers.}
  \label{fig:CMS}
\end{figure}

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=1 \columnwidth]{./fourlayers.png}
  \caption{ \onehalfspacing Fours layers of one double disk of TEPX showing module arrangement in rings for all layers.}
  \label{fig:CMS}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.8\columnwidth]{./coincidences.png}
  \caption{ \onehalfspacing Diagram showing modules overlap between the front and back layers of one double disk of TEPX that creates two fold coincidences in $\phi$ and r.}
  \label{fig:CMS}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.8\columnwidth]{./up.png}
  \caption{\onehalfspacing Left: View in the x-y plane of the double disk structure of one TEPX disk. The sensors in blue and red correspond to the two double disks at slightly different z positions. Right: Example of two- and threefold coincidence regions on a portion of a single TEPX disk.}
  \label{fig:CMS}
\end{figure}

@@

VdM (PU 0.5) $\:\:$  Trigger frequency (kHz) $\:\:$ 1 bx, 30 s $\:\:$ 100 bx, 30 s \\
TEPX D4R1 2x Coincidences in $\phi$  $\:\:$  800        $\:\:$   1.7         $\:\:$       0.17   \\
TEPX 2x Coincidences in $\phi$   $\:\:$     500        $\:\:$   0.485       $\:\:$       0.0485   \\

Physics (PU 200)  $\:\:$ Trigger frequency (kHz)   $\:\:$   1 bx, 4 LN (1.46 s)   $\:\:$     2500 bx, 1 LS (23 s)  \\
                                                      $\:\:$           ``Online''          $\:\:$           ``Offline''      \\
TEPX D4R1 2x Coincidences in $\phi$  $\:\:$   800                $\:\:$   0.386           $\:\:$            0.00193         \\
TEPX 2x Coincidences in $\phi$       $\:\:$   75           $\:\:$         0.284           $\:\:$            0.00142         \\

### 2021-05-14 project_ashish_monograph/vdM.tex
progress

\section{van der Meer calibration}
\label{sec:vdm}
Van der Meer (VdM) scans are done to calculate the visible cross section $\sigma_{vis}$ which is a calibration constant in the relation between rate of a quantity (clusters, coincidences) read out by the detector and the instantaneous luminosity. \\

@@

where $N_1, N_2$ are the number of protons in the colliding bunches, f is the LHC orbit frequency whose value is 11246Hz,  $\rho_1(x,y)$ and $\rho_2(x+\Delta x,y+\Delta y)$ are the two dimensional particle density distribution functions for each colliding bunch separated by $\Delta x$ and $\Delta y$. \\

@@

The VdM scan determines the beam overlap integrals $\int \rho_{x1} (x) \rho_{x2} (x+\Delta x) dx$ and  $\int \rho_{y1}(y) \rho_{y2} (y+\Delta y) dy$ by measuring pixel clusters rate as a function of bunch separation $\Delta x$ and $\Delta y$ along x and y directions as shown in Fig. 7. \\

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=\columnwidth]{./vdm_image.png}
  \caption{ \onehalfspacing }
  \label{fig:CMS}
\end{figure}

>>>>

\newpage \section{van der Meer calibration}
\label{sec:vdm}
Van der Meer (VdM) scans are done to calculate the visible cross section $\sigma_{vis}$ which is a calibration constant in the relation between rate of a quantity (clusters, coincidences) read out by the detector and the instantaneous luminosity. \\

@@

where $N_1, N_2$ are the number of protons in the colliding bunches, f is the LHC orbit frequency whose value is 11246Hz,  $\rho_1(x,y)$ and $\rho_2(x+\Delta x,y+\Delta y)$ are the two dimensional particle density distribution functions for each colliding bunch separated by $\Delta x$ and $\Delta y$ in the x and y directions. \\

@@

The VdM scan determines the bunch  overlap integrals $\int \rho_{x1} (x) \rho_{x2} (x+\Delta x) dx$ and  $\int \rho_{y1}(y) \rho_{y2} (y+\Delta y) dy$ by measuring pixel clusters rate as a function of bunch separation $\Delta x$ and $\Delta y$ along x and y directions as shown in Fig. 7. \\

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=\columnwidth]{./vdm_image.png}
  \caption{\onehalfspacing Figure showing two LHC bunches in green and blue approaching each other and colliding giving rise to an overlapping region showing in red whose area is determined during VdM scans.}
  \label{fig:CMS}
\end{figure}
